---
title: "Simple MixFishSim Example"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Simple MixFishSim Example}
    %\VignetteEngine{knitr::rmarkdown}
      \usepackage[utf8]{inputenc}
---

This is a simple example of how to use \textbf{'MixFishSim'} to generate simulations of dynamics in a mixed fishery.

# Load MixFishSim

```{r packages}
library(MixFishSim)
library(knitr)
opts_chunk$set(tidy = TRUE)

```

# Initialise the simulation

## Base parameters

First we specify the basic parameters of the simulation. This includes the size of the spatial domain, the number of years to simulate, the number of fleets and vessels per fleet and the number of species for the simulation etc... 

The object returned is used internally by MixFishSim a list with two objects: 

* sim$idx : The different units of different processes 
* sim$brk.idx: breaks for each of the key processes in units of a timestep

```{r basic}

sim <- init_sim(nrows = 20, ncols = 10, n_years = 10, n_tows_day = 4, n_days_wk_fished = 5, n_fleets = 2, n_vessels = 20, n_species = 2, move_freq = 2)

class(sim)
sim$idx
names(sim$brk.idx)

```

## Habitat setup

This function creates the spatial fields which support the fish populations and fisheries. You define the parameters for the mattern covariance function for each population and optionally the location of any spawning closure areas. 

It returns a list of suitable habitat for each species (hab), the habitat as adjusted during the spawning period (spwn_hab) and the binary location of spawning areas (spwn_loc). It also returns the locations as x1,x2,y1,y2 and the multiplier of attractiveness to the spawning area during spawning periods (spwn_mult).

If plot.dist = TRUE, it returns the plots to a file.

```{r habitat}

hab <- create_hab(sim_init = sim, 
		  spp.ctrl = list(
				  "spp.1" = list('nu' = 1/0.015,
						'var' = 1,
						'scale' = 1,
						'Aniso' = matrix(nc = 2, c(1.5, 3, -3, 4))),
				  "spp.2" = list('nu' = 1/0.05,
						'var'  = 2,
						'scale' = 12,
						'Aniso' = matrix(nc = 2, c(1, 2, -1, 2)))
				  ),
		  spawn_areas = list(
				     "spp1" = list(
						   'area1' = c(2,5,2,5),
						   'area2' = c(6,8,6,8)
						   ),
				     "spp2" = list(
						   'area1' = c(5,6,6,6)
						   ),
				     spwn_mult = 10, 
				     plot.dist = FALSE)
		  )

print(hab)

## Plot the unadjusted habitat fields
plot_habitat(hab$hab)

## Plot the adjusted habitat fields
plot_habitat(hab$spwn_hab)

```

## Population models

Now we need to set up the population models for the simulations. We do this
with the init_pop function. We set the initial population biomasses, movement
rates, recruitment parameter and growth and natural mortality rates.

The object created stores all the starting conditions and containers for the
changes in the populations during the simulations.

```{r pop_init}

Pop <- init_pop(sim_init = sim, Bio = c("spp1" = 1e5, "spp2" = 1e3),
		hab = hab[["hab"]], start_cell = c(5,5),
		lambda = c("spp1" = 0.1, "spp2" = 0.1),
		init_move_steps = 20,
		rec_params = list("spp1" = c("model" = "BH", "a" = 4, "b" = 2, "cv" = 0.7),
				  "spp2" = c("model" = "BH", "a" = 27, "cv" = 0.3)),
		rec_wk = list("spp1" = 3:6, "spp2" = 4:8),
		spwn_wk = list("spp1" = 4:8, "spp2" = 4:8),
		M = c("spp1" = 0.2, "spp2" = 0.2),
		K = c("spp1" = 0.3, "spp2" = 0.3)
		)

names(Pop)

Pop$dem_params

image(Pop$Start_pop[[1]], main = "spp1 starting biomass")
image(Pop$Start_pop[[2]], main = "spp2 starting biomass")
					   
```

## Population movement

Now we set up the population tolerance to different temperatures. We can then
plot the combined spatiotemporal suitable habitat.

```{r temp}

moveCov <- init_moveCov(sim_init = sim, steps = 52,
			spp_tol = list("spp1" = list("mu" = 12, "va" = 8),
				       "spp2" = list("mu" = 15, "va" = 7)
				       )
			)

plot(norm_fun(x = 0:25, mu = 12, va = 8)/max(norm_fun(0:25, 12, 8)), 
     type = "l", xlab = "Temperature", ylab = "Tolerance", lwd = 2)
lines(norm_fun(x = 0:25, mu = 15, va = 7)/ max(norm_fun(0:25, 15, 7)),
      type = "l", col = "blue", lwd = 2)
legend(x = 2, y = 0.9, legend = c("spp1", "spp2"), lwd = 2, col = c("black", "blue"))

plot_spatiotemp_hab(hab = hab, moveCov = moveCov, spwn_wk = list("spp1" = 4:8, "spp2" = 4:8))

```

## Fleet models

Here we initialise the fleet with fish landings price per tonne, catchability coefficients per population,
fuel cost, the coefficients for the step function and fleet behaviour.

We can plot the behaviour of the step function.

```{r fleets}

fleets <- init_fleet(sim_init = sim, VPT = list("spp1" = 4, "spp2" = 3),
		     Qs = list("fleet 1" = c("spp1" = 0.01, "spp2" = 0.03),
			       "fleet 2" = c("spp1" = 0.05, "spp2" = 0.01)
			       ),
		     fuelC = list("fleet1" = 3, "fleet 2" = 8),
		     step_params = list("fleet 1" = c("rate" = 3, "B1" = 1, "B2" = 2, "B3" = 3),
					"fleet 2" = c("rate" = 3, "B1" = 2, "B2" = 3, "B3" = 4)
					),				
		     past_knowledge = TRUE,
		     past_year_month = TRUE,
		     past_trip = TRUE,
		     threshold = 0.7
		     )

test_step(step_params = fleets$fleet_params[[1]]$step_params, rev.max = 1e2)
test_step(step_params = fleets$fleet_params[[2]]$step_params, rev.max = 1e2)

```


## Run simulation

```{r sim}

set.seed(123)

res <- run_sim(sim_init = sim,
	       pop_init = Pop,
	       move_cov = moveCov,
	       fleets_init = fleets,
	       hab_init = hab,
	       save_pop_bio = TRUE,
	       survey = NULL,
	       closure = NULL)



```




